NLO QCD+EW corrections to diphoton production in association with a vector boson

### 2017-10-25 results.tex
update xs table

In Table \ref{tab:xsec} we quote the inclusive cross sections for all 
three processes. 
The fiducial cuts for each process is detailed in its 
respective subsection below. 
We note that the NLO QCD corrections for both triple photon 
production and \aaw\ production are strongly jet veto dependent, 
a result that was previously discussed in great detail in 
\cite{Bozzi:2011en,Bozzi:2011wwa}, and will be revisited in the 
following. 
A much milder jet veto dependence is found for \aaz\ production. 
The electroweak corrections to inclusive cross sections are 
generally much smaller, ranging from ..\% (\aaa) to ..\% (\aaw) 
and ..\% (\aaz).

\begin{table}[t!]
  \centering
  \begin{tabular}{l||c|c|c}
      & $\;\;pp \to \gamma \gamma\gamma\;\;$
      & $\;\;pp \to \gamma \gamma e^-\bar\nu_e\;\;$ 
      & $\;\;pp \to \gamma \gamma e^+e^-\;\;$ \\
    \hline\hline
    $\sigma_\text{LO}\;\;[\text{pb}] $ &  &  & \\
    \hline
    $\delta_\text{QCD}\;\;[\text{pb}]\;\;\pTveto=\infty $ &  &  & \\
    \hline
    $\delta_\text{QCD}\;\;[\text{pb}]\;\;\pTveto=30\,\text{GeV} $ &  &  & \\
    \hline
    $\delta_\text{EW}\;\;[\text{pb}] $ &  &  & \\
  \end{tabular}
  \caption{
    Total cross sections at LO, NLO QCD and NLO EW for $\gamma\gamma\gamma$, 
    $\gamma\gamma e^-\bar\nu_e$ and $\gamma\gamma e^+e^-$
    production at 13\,TeV at the LHC.
    \label{tab:xsec}
  } 
\end{table}

@@

\begin{figure}[t!]
  \setlength{\unitlength}{\textwidth}
  \begin{picture}(0,0.37)
    \put(0,0.24){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/pT_y1}}
    \put(0,0.12){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/pT_y2}}
    \put(0,0){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/pT_l1l2_comb_log}}
    \put(0.33,0.24){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/m_y1y2_comb_log}}
    \put(0.33,0.12){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/m_y1l1l2_comb_log}}
    \put(0.33,0){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/m_y2l1l2_comb_log}}
    \put(0.66,0.24){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/dphi_y1_y2}}
    \put(0.66,0.12){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/dphi_y1_l1l2}}
    \put(0.66,0){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/dphi_y2_l1l2}}
  \end{picture}
  \caption{
    Contribution of $\gamma\gamma$-induced production channels at LO.
    \label{fig:aaz:aa-ind}
  }
\end{figure}

>>>>

In Table \ref{tab:xsec} we quote the inclusive cross sections for all 
three processes. 
The fiducial cuts for each process is detailed in its 
respective subsection below. 
We note that the NLO QCD corrections for both triple photon 
production and \aaw\ production are strongly jet veto dependent, 
a result that was previously discussed in great detail in 
\cite{Bozzi:2011en,Bozzi:2011wwa}, and will be revisited in the 
following. 
A much milder jet veto dependence is found for \aaz\ production. 
The electroweak corrections to inclusive cross sections are 
generally much smaller, ranging from $0.6\%$ (\aaa) to $-1.8\%$ (\aaw) 
and $-4.6\%$ (\aaz).

\begin{table}[t!]
  \input{xs}
  \caption{
    Total cross sections at LO, NLO QCD and NLO EW for $\gamma\gamma\gamma$, 
    $\gamma\gamma e^-\bar\nu_e$ and $\gamma\gamma e^+e^-$
    production at 13\,TeV at the LHC.
    \label{tab:xsec}
  } 
\end{table}

@@

\begin{figure}[t!]
  \setlength{\unitlength}{\textwidth}
  \begin{picture}(0,0.37)
    \put(0,0.24){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/pT_y1}}
    \put(0,0.12){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/m_y1y2_comb_log}}
    \put(0,0){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/dphi_y1_y2}}
    \put(0.33,0.24){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/pT_y2}}
    \put(0.33,0.12){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/m_y1l1l2_comb_log}}
    \put(0.33,0){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/dphi_y1_l1l2}}
    \put(0.66,0.24){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/pT_l1l2_comb_log}}
    \put(0.66,0.12){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/m_y2l1l2_comb_log}}
    \put(0.66,0){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/dphi_y2_l1l2}}
  \end{picture}
  \caption{
    Contribution of $\gamma\gamma$-induced production channels at LO.
    \label{fig:aaz:aa-ind}
  }
\end{figure}
